---
title: "Lab 8"
author: "Mari Herbst"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

### Create a subset with 4 cities

Task: create a subset called homes_subset that only contains observations where the city is:

- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>%
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status using homes_subset

*{eval = FALSE} means code will not even be run. {include = FALSE} means code will be run but won't show up in knitted version*

```{r}
homes_subset %>%
  group_by(City, Status) %>%
  summarize(price_mean = mean(Price),
            price_sd = sd(Price))
```

Task: explore the relationship between square footage and home price (from home_subset) in a scatterplot

- positive linear relationship between square footage and home price

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Create different versions of this model:

1. Price ~ City, Bedrooms, Bathrooms, SqFt, Status (lm1)
2. Price ~ City, SqFt, Status (lm2)
3. dealer's choice (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)

lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)

lm3 <- lm(Price ~ City + Bedrooms + Bathrooms, data = homes_subset)

# If I wanted San Luis Obispo to be the reference level, use fct_relevel to specify a new reference level
new_homes_subset <- homes_subset %>%
  mutate(City = fct_relevel(City, "San Luis Obispo"))

# This will use SLO as the reference level for city
lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)
```

R$^2$ = how much of variance in dependent variable is predicted by this model

### Explore correlations between quantitative variables

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFt

```{r}
homes_quant <- homes_subset %>%
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse") # use method = to change how correlation is visualized
```

### Compare AIC values

AIC: compares model fit vs complexity. lower AIC indicates a better balance

```{r}
AIC(lm1)
AIC(lm2)
```

### Use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Check out diagnostic plots for lm1

```{r}
plot(lm1)
```

Cook's distance > 1 means a data point is pulling disproportionately

### Use broom::augment() to return the predictions for existing observations

".fitted" column indicates the price our model would predict the price to be

```{r}
home_predictions <- augment(lm1)
```

### Make a histogram of the residuals from this model (lm1)

```{r}
ggplot(data = home_predictions, aes(x = .resid)) +
  geom_histogram()
```

